%\documentclass{article}
\documentclass{scrartcl}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{algorithmic}
\usepackage{algorithm}
\usepackage{xcolor}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Note Block - source: https://tex.stackexchange.com/questions/94464/note-environment-with-mdframed
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\usepackage[framemethod=default]{mdframed}

%\global\mdfdefinestyle{exampledefault}{%
%linecolor=lightgray,linewidth=1pt,%
%leftmargin=0cm,rightmargin=0cm,
%}

\newcommand{\fl}{\text{fl}}
\newcommand{\op}{\text{ op }}

\newenvironment{mymdframed}[1]{%
\mdfsetup{%
frametitle={\colorbox{white}{\,#1\,}},
frametitleaboveskip=-\ht\strutbox,
frametitlealignment=\raggedright
}%
\begin{mdframed}[style=exampledefault]
}{\end{mdframed}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\title{Homework Sheet 1}
\subtitle{VU Numerical Algorithms, SoSe 2018}
\date{\underline{\emph{due date: 23.4.2018, 18:00}}}

\begin{document}

\maketitle

%        \begin{mymdframed}{Submission Guidelines}
            \begin{itemize}
                \item Please submit an anonymized version of your report without your name or your Matrikelnummer appearing in the document. 
            \end{itemize}
%        \end{mymdframed}

\section*{Prerequisites}
\begin{enumerate}
	\item Basics:
	\begin{itemize}
		\item No global variables allowed.
		
		\item Pay attention to the interface definitions (i.e., use the specified terms! In/output parameters must be in the specified order!)
		\item Your routines should always check the number and types of input arguments.
		\item Do not plot results in predefined routines! Plot results in scripts or self defined routines only.
		\item[x] (Produce separate routines (i.\,e., for Part I: preparation of the input matrices, $LU$ decomposition). Write modular code! Use consistent interfaces for your routines.)
	\end{itemize}
	\item Submission:	
	\begin{itemize}		
		\item  Upload a single zip archive with all your source code files and your report (as a single
			PDF file named \textit{report.pdf} with all plots and discussions of results) on the course page in Moodle.
		\item Name your archive \texttt{a$<$matriculation number$>$.zip} (e.g. \textit{a01234567.zip})
		\item Directories in the archive are not allowed.
		\item A complete submission should include the following files:
		\begin{enumerate}
		\item Routines: \textit{accuracy.m, linSolve.m, plu.m, solveL.m, solveU.m}, self defined routines (optional)
		\item Scripts: \textit{part1.m, part2.m, part3.m}
		\item Documentation: \textit{report.pdf}
		\end{enumerate}
		
		\end{itemize}
	\end{enumerate}
\end{document}
