%\documentclass{article}
\documentclass{scrartcl}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{algorithmic}
\usepackage{algorithm}
\usepackage{xcolor}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Note Block - source: https://tex.stackexchange.com/questions/94464/note-environment-with-mdframed
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\usepackage[framemethod=default]{mdframed}

%\global\mdfdefinestyle{exampledefault}{%
%linecolor=lightgray,linewidth=1pt,%
%leftmargin=0cm,rightmargin=0cm,
%}

\newcommand{\fl}{\text{fl}}
\newcommand{\op}{\text{ op }}

\newenvironment{mymdframed}[1]{%
\mdfsetup{%
frametitle={\colorbox{white}{\,#1\,}},
frametitleaboveskip=-\ht\strutbox,
frametitlealignment=\raggedright
}%
\begin{mdframed}[style=exampledefault]
}{\end{mdframed}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\title{Homework Sheet 1}
\subtitle{VU Numerical Algorithms, SoSe 2019}
\date{\underline{\emph{due date: 23.4.2019, 18:00}}}

\begin{document}

\maketitle

%        \begin{mymdframed}{Submission Guidelines}
%            \begin{itemize}
%                \item Please submit an anonymized version of your report without your name or your Matrikelnummer appearing in the document. 
%            \end{itemize}
%        \end{mymdframed}


\section*{Programming Exercise}
    The task is to implement an LU factorization-based linear solver in OCTAVE and to evaluate its accuracy for various test matrices. The solver consists of computing the LU decomposition of a square $n \times n$ double precision matrix $A$ such that $A = LU$ with lower triangular $L$ and upper triangular $U$ and subsequent forward and back substitution. In particular:
        
    \subsection*{Part I - LU Decomposition (3 points)}
        First implement the standard "scalar" (unblocked) algorithm (i.e. three nested loops) \textbf{with partial pivoting}.
        
        \begin{algorithm}
            \caption{Pseudo-Code LU Decomposition with partial pivoting}
            \begin{algorithmic}\label{alg:plu}
                \FOR {$k=1$ to $n-1$}
                    \STATE Find index $p$ such that
                    \STATE $|a_{pk}| \geq |a_{ik}| \; for \; k \leq i \leq n$
                    \IF {$p \neq k$}
                        \STATE interchange rows $k$ and $p$
                    \ENDIF
                    \IF {$a_{kk} = 0$}
                        \STATE continue with next $k$
                    \ENDIF
                    \FOR {$i=k+1$ to $n$}
                        \STATE $m_{ik} = a_{ik} / a_{kk}$
                    \ENDFOR
                    \FOR {$j=k+1$ to $n$}
                        \FOR {$i=k+1$ to $n$}
                            \STATE $a_{ij} = a_{ij} - m_{ik}a_{kj}$
                        \ENDFOR
                    \ENDFOR
                \ENDFOR
            \end{algorithmic}
        \end{algorithm}
    
%        \begin{mymdframed}{Note}
            \begin{itemize}
%                \item Also implement partial pivoting (not shown in the pseudo-code).
                \item $U$ is contained in the upper triangle (plus diagonal) of $A$, and the diagonal entries of $L$ are all 1. The subdiagonal entries of $L$ are given by the scalars $m_{ik}$ (i.e. $L(i,k) = m_{ik}$). For storage efficiency, we can store $L$ in the lower triangle of $A$, and thus $A(i,k)$ has to be overwritten with $m_{ik}$ (see Algorithm~\ref{alg:plu}).
            \end{itemize}
%        \end{mymdframed}
    
    \subsubsection*{Detailed remarks:}
    \begin{enumerate}
        \item \textit{Accuracy}: Verify the correctness of your $LU$ factorization by evaluating the relative residual
        \begin{align*}
            R = \frac{\|P^TLU - A\|_{1}}{\|A\|_{1}}
        \end{align*}
        where $\|\cdot\|_{1}$ is the maximum absolute column sum of a matrix:
        \begin{align*}
            \|M\|_{1} = \underset{j = 1, \dots, n}{max} \; \sum_{i=1}^{n} |M_{ij}|
        \end{align*}
        
        Plot these residuals $R$ for all problem sizes you experimented with.
        \emph{When plotting residuals, always use a \textbf{logarithmic scale} along the \textbf{y-axis}!}
        
        \item Use randomly generated matrices $A$ as input, but please specify clearly in your report how you generated your test matrices!
        
%        \item Produce separate routines (i.\,e., preparation of the input matrices, $LU$ decomposition). Write modular code! Use consistent interfaces for your routines:
%        \begin{enumerate}
%            \item Input: $A, n$
%            \item Output: $n \times n$ matrices $L$ and $U$ stored in the array $A$ ($A=LU$) and the permutation matrix $P$.
%        \end{enumerate}
        
    %    \item \textit{Report}: Summarize your work in a written report, summarizing your measurements and an interpretation of your results.
        
%        \item What is NOT allowed:
%            \begin{enumerate}
%                \item Do not use any existing code which you did not write yourself!
%                \item Do not try to exploit any special structure in the input data. The code has to be generic and should run for all possible input matrices $A$.
%            \end{enumerate}
    \end{enumerate}
    
    \subsection*{Part II - Solving a Triangular Linear Systems (1 point)}
        \begin{enumerate}
            \item \textbf{Forward substitution}: Write a routine which solves a given $n \times n$ lower triangular linear system $Lx = b$ for $x$.
            \item \textbf{Back substitution}: Write another routine which solves a given $n \times n$ upper triangular linear system $Ux = b$ for $x$.
            \item Evaluate the accuracy of your codes for increasing $n$ in terms of the relative residual and the relative forward error. \emph{(For the definition of relative residual and relative forward error please see Part III!)}
            
            For these experimental evaluations, use randomly generated (non-singular) $L$ and $U$ and determine $b$ such that the exact solution $x$ is a vector of all ones: $x = (1, 1, \dots, 1, 1)^{T}$.  
        \end{enumerate}

    \subsection*{Part III - Numerical Accuracy of LU-Based Linear Solver (4 points)}
    The main purpose of this part is to experimentally evaluate the numerical accuracy of the linear systems solver you implemented in Parts I and II for different test matrices and to compare it with the built-in solver from OCTAVE. 
    You can solve a linear system $Ax=b$ for $x$ using the $\setminus$ operator (e.g. $x = A \setminus b$).
 
    \begin{enumerate}
        \item Take your LU factorization from Part I and combine it with your triangular linear systems solvers from Part II in order to get a complete LU-based linear solver.
        \item Input data for your experiments:
        \begin{enumerate}
            \item Generate random test matrices $S$ with entries uniformly distributed in the interval [-1,1].
            \item Generate test matrices $H$ which are defined by
            \begin{align*}
                H_{ij} := \frac{1}{i+j-1} \quad for \;i=1,\dots,n \; \mbox{and} \; j=1, \dots, n.
            \end{align*}
            \item In all your test cases, determine the corresponding right hand side $b$ of length $n$ such that the exact solution $x$ of the linear system is a vector of all ones: $x = (1, 1, \dots, 1, 1)^{T}$.
        \end{enumerate}
        \item Solve the linear systems $Sx = b$ and $Hx=b$ with your LU-based linear solver and the built-in OCTAVE solver and evaluate the numerical accuracy of the computed solution.
        \begin{enumerate}
            \item \textit{Problem sizes}: Start with $n=2,3,4,5,\dots,10$ then incease in increments of $5$. For $n > 50$ you can further increase the increment. The largest value of $n$ should be as large as possible (so that your code terminates within a reasonable time).
            \item \textit{Accuracy}: For the computed solution $\hat{x}$, evaluate the relative residual $r$:
            \begin{align*}
                r := \frac{||M\hat{x} - b||_1}{||b||_1}
            \end{align*}
            ($M$ is $S$ or $H$)
            as well as the relative forward error $f$:
            \begin{align*}
                f := \frac{||\hat{x} - x||_1}{||x||_1}. 
            \end{align*}
        \end{enumerate}
        \item For both your and the OCTAVE solver generate the following plots for the different test matrices:
            \begin{enumerate}
            \item Relative residual and relative forward error in $\hat{x}$ vs. $n$: One figure for both accuracy metrics for matrix type $S$, another figure for both accuracy metrics for matrix type $H$.
            \end{enumerate}
        \item Interpret and explain your experimental results in your report. Do you think that there is a fundamental difference in the numerical accuracy which your LU-based linear solver achieves for the two types of test matrices? If yes, explain the reasons for this difference. How does your solver compare to the OCTAVE version?
    \end{enumerate}
\end{document}
